Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-18 paper/ms.tex
update acknowledge

@@

\acknowledgments
LGB gratefully acknowledges support from the Heising-Simons
51~Pegasi~b Fellowship.  A few thank-yous in particular (from LGB) are
owed to G.~Laughlin, A.~Mann, and J.~Spake for clarifications and
ideas, and to E.~Schaller and the 51 Peg science team for organizing
the annual summits.  In addition, this paper relied on data collected
by the TESS mission, which are publicly available from the Mikulski
Archive for Space Telescopes (MAST).  Funding for the TESS mission is
provided by NASA’s Science Mission Directorate.  TIC 402980664 in
particular was observed at 120-second cadence thanks to the TESS Guest
Investigator programs G022252 (PI: J.~Schlieder; Sectors 18, 19, 25,
26) and G04168 (PI: R.~Jayaraman; Sector 53).

%{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
LGB conceived the project and performed the dip-counting search, light
curve classification, cluster membership, SED, variability, and
secondary-period analyses.
RJ and SR performed the Fourier-based analysis and contributed
to light curve classification.
LR cross-examined the light curve classification, and contributed an independent SED analysis.
AD identified the magnetic B star connection.
LAH contributed to project design and to the interpretation of the light curves.
G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
GRR is an architect of the TESS mission.
{\bf JNW?  MNG?}
All authors assisted in manuscript writing and revision.

>>>>

\author[0000-0002-0531-1073]{H. Isaacson}
\affiliation{\berkeley}

\author[0000-0001-8638-0320]{A. W. Howard}
\affiliation{\caltech}

@@

\acknowledgments
LGB is grateful for support from the Heising-Simons 51~Pegasi~b
Fellowship.  A few thank-yous (from LGB) are owed to G.~Laughlin,
A.~Mann, and J.~Spake for clarifications and ideas, and to E.~Schaller
and the 51 Peg science team for organizing the annual summits.  In
addition, this paper relied on data collected by the TESS mission,
which are publicly available from the Mikulski Archive for Space
Telescopes (MAST).  Funding for the TESS mission is provided by NASA’s
Science Mission Directorate.  TIC 402980664 in particular was observed
at 120-second cadence thanks to the TESS Guest Investigator programs
G022252 (PI: J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI:
R.~Jayaraman; Sector 53).

%{\bf AUTHOR CONTRIBUTION STATEMENTS: PLEASE REVISE IF APPROPRIATE)}
LGB conceived the project and performed the dip-counting search, light curve classification, cluster membership, SED, variability, and secondary-period analyses.
RJ and SR performed the Fourier-based analysis and contributed to light curve classification.
LR cross-examined the light curve classification, and contributed an independent SED analysis.
AD identified the magnetic B star connection.
LAH contributed to project design and to the interpretation of the light curves.
G\'AB acquired and maintained the servers used to run the dip-finding pipeline.
-----
{\bf JNW, MNG, GRR, HI, and AH to confirm coauthorship \&/or to help out on interpretation!}
HI and AH designed and maintain the architecture used to acquire and process the HIRES spectra.
All authors assisted in manuscript writing and revision.
